Mathematical Description

### 2023-06-15 100-math-description/GR-sslcm-math-description.Rmd
More improvements for docx output

---
title: "\\textsc{Mathematical Description}"
subtitle: "\\textsc{State-Space Life Cycle Model for Grande Ronde Spring Chinook Salmon}"
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: true
    toc_depth: 3
    number_sections: true
    citation_package: natbib
  # bookdown::word_document2
fontfamily: mathpazo
geometry: [top=1in,bottom=1in,left=0.25in,right=1.75in]
linkcolor: cyan
urlcolor: cyan
citecolor: black
bibliography: cites.bib
link-citations: true
biblio-style: apalike
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{microtype}
  - \usepackage{float}
  - \usepackage{xcolor}
  - \definecolor{my-blue}{HTML}{E6F0FF}
  - \usepackage[textwidth=1.5in]{todonotes}
  - \setuptodonotes{backgroundcolor=my-blue,textcolor=black,linecolor=ProcessBlue,bordercolor=my-blue,size=footnotesize}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \cfoot{\thepage}
  - \renewcommand{\headrulewidth}{0.5pt}
  - \renewcommand{\footrulewidth}{0.5pt}
  - \lfoot{State-Space Life Cycle Model\\Mathematical Description}
  - \rfoot{Grande Ronde Spring Chinook Salmon}
  - \usepackage{titlesec}
  - \titleformat{\section}{\bfseries\LARGE\scshape}{\thesection}{1em}{}
  - \titleformat{\subsection}{\bfseries\large}{\thesubsection}{1em}{}
  - \titleformat{\subsubsection}{\itshape}{\thesubsubsection}{1em}{}
  - \renewcommand{\contentsname}{Table of Contents}
  - \renewcommand{\eqref}[1]{\ref{#1}}
  - \renewcommand*{\log}{\mathrm{log}\hspace{-0.20em}}
  - \renewcommand*{\max}{\mathrm{max}\hspace{-0.20em}}
  - \newcommand{\logit}{\mathrm{logit}\hspace{-0.20em}}
  - \newcommand{\ilogit}{\mathrm{logit}^{-1}\hspace{-0.20em}}
  - \newcommand{\MVNdist}{\mathcal{MVN}\hspace{-0.20em}}
  - \newcommand{\Ndist}{\mathcal{N}\hspace{-0.20em}}
  - \newcommand{\Bdist}{\mathcal{B}\hspace{-0.20em}}
  - \newcommand{\Mdist}{\mathcal{M}\hspace{-0.20em}}
  - \newcommand{\fall}{\mathrm{fall}}
  - \newcommand{\spring}{\mathrm{spring}}
  - \newcommand{\NOR}{\mathrm{NOR}}
  - \newcommand{\HOR}{\mathrm{HOR}}
  - \newcommand{\CAT}{\mathrm{CAT}}
  - \newcommand{\LOS}{\mathrm{LOS}}
  - \newcommand{\MIN}{\mathrm{MIN}}
  - \newcommand{\UGR}{\mathrm{UGR}}
  - \newcommand{\WUL}{\mathrm{WUL}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
```

@@

@@

@@

@@

@@

\listoftodos

# References {-}

>>>>

---
title: "Mathematical Description"
subtitle: "State-Space Life Cycle  Model for Grande Ronde Spring Chinook Salmon"
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: true
    toc_depth: 3
    number_sections: true
    citation_package: natbib
  # bookdown::word_document2
fontfamily: mathpazo
geometry: [top=1in,bottom=1in,left=0.25in,right=1.75in]
linkcolor: cyan
urlcolor: cyan
citecolor: black
bibliography: "GR-sslcm-cites.bib"
link-citations: "`r ifelse(knitr::is_latex_output(), 'true', 'false')`"
biblio-style: apalike
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/canadian-journal-of-fisheries-and-aquatic-sciences.csl"
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{microtype}
  - \usepackage{float}
  - \usepackage{xcolor}
  - \definecolor{my-blue}{HTML}{E6F0FF}
  - \usepackage[textwidth=1.5in]{todonotes}
  - \setuptodonotes{backgroundcolor=my-blue,textcolor=black,linecolor=ProcessBlue,bordercolor=my-blue,size=footnotesize}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \cfoot{\thepage}
  - \renewcommand{\headrulewidth}{0.5pt}
  - \renewcommand{\footrulewidth}{0.5pt}
  - \lfoot{State-Space Life Cycle Model\\Mathematical Description}
  - \rfoot{Grande Ronde Spring Chinook Salmon}
  - \usepackage{titlesec}
  - \titleformat{\section}{\bfseries\LARGE\scshape}{\thesection}{1em}{}
  - \titleformat{\subsection}{\bfseries\large}{\thesubsection}{1em}{}
  - \titleformat{\subsubsection}{\itshape}{\thesubsubsection}{1em}{}
  - \renewcommand{\contentsname}{Table of Contents}
  - \renewcommand{\eqref}[1]{\ref{#1}}
  - \newcommand{\fall}{\mathrm{fall}}
  - \newcommand{\spring}{\mathrm{spring}}
  - \newcommand{\NOR}{\mathrm{NOR}}
  - \newcommand{\HOR}{\mathrm{HOR}}
  - \newcommand{\CAT}{\mathrm{CAT}}
  - \newcommand{\LOS}{\mathrm{LOS}}
  - \newcommand{\MIN}{\mathrm{MIN}}
  - \newcommand{\UGR}{\mathrm{UGR}}
  - \newcommand{\WUL}{\mathrm{WUL}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
library(officedown)
```

@@

```{r bookdown-post-latex, eval = TRUE}
# https://github.com/rstudio/bookdown/issues/8#issuecomment-564689497
# easy method of placing bibliography somewhere other than at the end of the document always
options(bookdown.post.latex = function(x) {

  # x is the content of the LaTeX output file
  # str_replace can take a named vector of patterns and replacements
  replace_patterns <- c(
    "\\\\bibliography\\{GR-sslcm-cites.bib\\}" = "",         # Remove the default bibliography
    "^BIB HERE$" = "\\\\bibliography{GR-sslcm-cites.bib}"    # Add it in a new spot
  )

  stringr::str_replace_all(x, replace_patterns)
})
```

```{r highlight-fn}
highlight = function(note) {
  if (knitr::is_latex_output()) {
    paste0("\\hl{", note, "}")
  } else {
    ft = officer::fp_text(shading.color = "yellow", font.family = "Times New Roman", font.size = 11)
    officer::ftext(toString(note), prop = ft)
  }
}
```

```{r new-commands, results = "asis"}
# these are shortcut math mode commands
# the hspace helps the appearance in latex, but it won't render to word
# the code below removes it if rendered to word output
commands = c(
  "\\renewcommand*{\\log}{\\mathrm{log}\\hspace{-0.20em}}",
  "\\renewcommand*{\\max}{\\mathrm{max}\\hspace{-0.20em}}",
  "\\newcommand{\\logit}{\\mathrm{logit}\\hspace{-0.20em}}",
  "\\newcommand{\\ilogit}{\\mathrm{logit}^{-1}\\hspace{-0.20em}}",
  "\\newcommand{\\MVNdist}{\\mathcal{MVN}\\hspace{-0.20em}}",
  "\\newcommand{\\Ndist}{\\mathcal{N}\\hspace{-0.20em}}",
  "\\newcommand{\\Bdist}{\\mathcal{B}\\hspace{-0.20em}}",
  "\\newcommand{\\Mdist}{\\mathcal{M}\\hspace{-0.20em}}"
)

if (!is_latex_output()) {
  commands = stringr::str_remove(commands, "\\\\hspace\\{-0\\.20em\\}")
}

cat(commands, sep = "\n")
```

@@

`r if (is_latex_output()) "BIB HERE"`

`r if (is_latex_output()) "\\newpage"`

@@

`r if (is_latex_output()) "\\newpage"`

@@

if (!is_latex_output()) {
  tab$Description = stringr::str_replace_all(tab$Description, "``", '"')
  tab$Description = stringr::str_replace_all(tab$Description, "''", '"')
}

@@

\newpage
`r if (!is_latex_output()) "# References {-}"`
